{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-12-01 wacv_for_review.tex
Some Comments Added

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to performance comparison with other trackers, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For the fair comparison, we did
not use the particle filter. The combination presented at the $2^{nd}$
column switched the order of deploying $R_{t}^{L}$ and
$R_{t}^{S}$. The one at the $3^{th}$ column removed $R_{t}^{S}$ and
replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The combinations with the ``*'' marker ran the
filters on every frame in the listed order. The trackers at the
$7^{th}$ and $8^{th}$ columns ran a translation and a scale filter on
every frame which is similar to the LCT tracker
\cite{ma2015long}.\footnote{To be precise, the LCT tracker comes with
  a re-detection module for a long-term tracking.} This experiment
empirically verified that \textit{E}nKCF is an optimal way of using
multiple KCFs, in terms of both tracking accuracy and run-time
performance. For example, we could achieve $4.26\%$ higher in accuracy
by running $R_{t}^{L}$ and $R_{S}$ at every frame, but this
combination decreases run-time performance to 317 fps.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} We were curious about
how the frame rate of a testing video would affect the performance of
a tracking algorithm. To this end, we use the temporarily down-sampled version
of the UAV123, called UAV123$\_$10fps dataset. We believe the downsampling
would make the original UAV123 data more challenging because the
displacements of the moving objects become even bigger. To tackle this challenge, w
e slightly modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
removed the particle filter. Figure \ref{fig:UAV123_10fpsDATASET}
shows the performance of the modified version of {\it E}nKCF and other
tracking methods. The precision rates of the ECO and CCOT dropped
about $10\%$ in comparison to the original UAV123 dataset. Our tracker
outperforms other high-speed correlation filter based trackers
including KCF, DSST by about $15\%$-$20\%$ and showed a precision rate
similar to that of SAMF. It ranks as fourth in AUC while running about
$10$ to $100$ times faster than the top three trackers. 
\textit{YoungWoo : I did not get this part clearly. How sensitive the frame rate 
or how sensitive the tracker is
?} It was interesting to observe how sensitive the frame rate is to the
performance of the state-of-the-art tracking algorithms, and, with a
slight modification, the proposed method effectively handled large
displacement of objects in successive frames.

>>>>

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to performance comparison with other trackers, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. To achieve fair comparison, we did
not use the particle filter. The combination presented at the $2^{nd}$
column switched the order of deploying $R_{t}^{L}$ and
$R_{t}^{S}$. The one at the $3^{th}$ column removed $R_{t}^{S}$ and
replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The combinations with the ``*'' marker ran the
filters on every frame in the listed order. The trackers at the
$7^{th}$ and $8^{th}$ columns ran a translation and a scale filter on
every frame which is similar to the LCT tracker
\cite{ma2015long}.\footnote{To be precise, the LCT tracker comes with
  a re-detection module for a long-term tracking.} This experiment
empirically verified that \textit{E}nKCF is an optimal way of using
multiple KCFs, in terms of both tracking accuracy and run-time
performance. For example, one could achieve $4.26\%$ higher in accuracy
by running $R_{t}^{L}$ and $R_{S}$ at every frame, but this
combination decreases run-time performance to 317 fps.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} We were curious about
how the frame rate of a testing video would affect the performance of
a tracking algorithm. To this end, we use the temporarily down-sampled version
of the UAV123, called UAV123$\_$10fps dataset. We believe the downsampling
would make the original UAV123 data more challenging because the
displacements of the moving objects become even bigger. To tackle this challenge, we 
slightly modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
removed the particle filter due to larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET}
shows the performance of the modified version of {\it E}nKCF and other
tracking methods. The precision rates of the ECO and CCOT dropped
about $10\%$ in comparison to the original UAV123 dataset. Our tracker
outperforms other high-speed correlation filter based trackers
including KCF, DSST by about $15\%$-$20\%$ and showed a precision rate
similar to that of SAMF. It ranks as fourth in AUC while running about
$10$ to $100$ times faster than the top three trackers. 
\textit{YoungWoo : I did not get this part clearly. How sensitive the frame rate 
or how sensitive the tracker is
?} It was interesting to observe how sensitive the frame rate is to the
performance of the state-of-the-art tracking algorithms, and, with a
slight modification, the proposed method effectively handled large
displacement of objects in successive frames. 
\textit{YoungWoo : I also believe that we should emphasize how the state-of-the-art
trackers perform in lower frame rates. And I believe this is what this paper \cite{mueller2017context}
says. They rank the trackers by evaluating them on videos matching their fps. I was thinking of running 
ECO and CCOT in UAV123 in 5 fps videos and mention how they degrade with respect to the decreasing fps.
I believe this is our contribution and we should emphasize it.}
